### 2019-07-25 chapters/4-approach.tex
Add blacklisted modules figure

This Thesis introduces a \textit{TypeScript Declaration Files Generation Method}, which generates a valid TypeScript Declaration File for a specific NPM package, as explained in Fig. \ref{fig:tsd_generation_method_block_diagram}.

@@

\subsubsection{Wrapper Objects}
\todo{Proxy Objects}
\todo{Primitives}
\todo{Null}
\todo{Undefined}
\subsection{Output Format}
\todo{Explicar que es un JSON con todas las interactions. Explicar estructura de cómo se forma el JSON}
\subsection{Blacklisted Modules}
\todo{Incluir grafico con los blacklisted modules}

>>>>

This Thesis introduces a \textit{TypeScript Declaration Files Generation Method}, which generates a valid TypeScript Declaration File for a specific NPM package, as explained in \figref{fig:tsd_generation_method_block_diagram}.

@@

\subsubsection{Wrapper Objects}
\todo{Proxy Objects}
\todo{Primitives}
\todo{Null}
\todo{Undefined}
\subsection{Output Format}
\todo{Explicar que es un JSON con todas las interactions. Explicar estructura de cómo se forma el JSON}
\subsection{Blacklisted Modules}
\input{figures/approach/blacklisted-modules/blacklistedModules.tex}
\todo{Incluir grafico con los blacklisted modules}
